---
title: ""
---

<!--Add a loading bar!-->
<script src="pace.js"></script>
<link href="pace_loadbar_loading.css" rel="stylesheet" />

<!--Create a block for title and breadcrumbs to appear on same line-->
<div style="width: 100%; display: inline-block;">
<div style="float: left;">
<h1>Dog Vaccination</h1>
</div>
<div style="float: right;">
<ol class="breadcrumb" style="background-color:white;">
  <li class="breadcrumb-item"><a href="index.html">Home</a></li>
  <li class="breadcrumb-item active">Dog Vaccination</li>
</ol>
</div>
</div>
<hr class="hr-orange">

<br>
  
<!--Begin page content!-->  

### Data {.tabset .tabset-pills}    
  
#### Serengeti: 2002 - present (annual)  
```{r, echo=FALSE, warning=FALSE, fig.width=10}
start_date <- "2001-12-31"
end_date <- Sys.Date()
dog_vac_barplot(dataframe=dog_vacc_data, type="all", start_date=start_date, end_date=end_date)
```
  
<br>
  
<hr class="hr-grey">

#### Serengeti: 2015 - present (monthly)    
```{r, echo=FALSE, warning=FALSE, fig.width=10}
start_date <- "2014-12-31"
end_date <- Sys.Date()
dog_vac_barplot(dataframe=dog_vacc_data_subset, type="subset", start_date=start_date,
                end_date=end_date)
```

<br>

<hr class="hr-grey">

### Village-level Vaccination Coverage  
  
The map details villages that were vaccinated (1 or more times) in Serengeti District from 2014-2019; where villages were visited multiple times in the same year, the date and Kitongoji (sub-village) are given. Select from the dropdown menu to view a specific year:  

```{r droplink, echo=FALSE}
# Create table
table_site <- c("html/ser_vacc_map_2019.html", "html/ser_vacc_map_2018.html", "
                html/ser_vacc_map_2017.html", "html/ser_vacc_map_2016.html", 
                "html/ser_vacc_map_2015.html", "html/ser_vacc_map_2014.html")
names(table_site) <- c("2019", "2018", "2017", "2016", "2015", "2014")

bsselect(table_site, type = "iframe", frame_height="550", style="btn-primary", show_tick=TRUE, height=0)
```
