---
title: ""
---

<!--Add a loading bar!-->
<script src="pace.js"></script>
<link href="pace_loadbar_loading.css" rel="stylesheet" />

<!--Create a block for title and breadcrumbs to appear on same line-->
<div style="width: 100%; display: inline-block;">
<div style="float: left;">
<h1>Rabies Incidence</h1>
</div>
<div style="float: right;">
<ol class="breadcrumb" style="background-color:white;">
  <li class="breadcrumb-item"><a href="index.html">Home</a></li>
  <li class="breadcrumb-item active">Rabies Incidence</li>
</ol>
</div>
</div>
<hr class="hr-orange">

<br>
  
<!--Begin page content!-->

```{r, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
script_district = "Serengeti"
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Set plot params
start_date_1 <- "2001-12-31"
start_month_1 <- 1
start_date_2 <- "2011-12-31"
diff_in_days = difftime(strptime(start_date_2, format = "%Y-%m-%d"), strptime(start_date_1, format = "%Y-%m-%d"), units = "days")
start_month_2 <- (floor(as.double(diff_in_days)/365))*12 
end_date <- Sys.Date()

# Find maximum number of bitten animals/bite victims for y-axis for each district
y_axis_max_2002 <- find_y_max(human_dataframe=human_epi_month, animal_dataframe=animal_epi_month, start_month=start_month_1, type="epi")
y_axis_max_2012 <- find_y_max(human_dataframe=human_epi_month, animal_dataframe=animal_epi_month, start_month=start_month_2, type="epi")
```
  
### Comparison of exposures and cases {.tabset .tabset-pills}   
  
#### 2002 to present  
``` {r, echo=FALSE, fig.width=10}
epi_plot(human_dataframe=human_epi_month, animal_dataframe=animal_epi_month,
         district=script_district, start_date=start_date_1, start_month=start_month_1,
         end_date=end_date, max_y=y_axis_max_2002)
```

<hr class="hr-grey">
  
#### 2012 to present  
``` {r, echo=FALSE, fig.width=10}
epi_plot(human_dataframe=human_epi_month, animal_dataframe=animal_epi_month, 
         district=script_district, start_date=start_date_2, start_month=start_month_2,
         end_date=end_date, max_y=y_axis_max_2012)
```

<hr class="hr-grey">
  
### Location of animal Rabies cases  
  
The map below shows the location of probable and lab-confirmed animal rabies cases traced in Serengeti District over the last five years.  This map excludes all bites where the rabies status is not suspect or cannot be determined; village centroids are used in the absence of coordinates. Select from the dropdown menu to view data from a specific year:  

```{r droplink, echo=FALSE}
# Create table
table_site <- c("html/ser_epi_map_2019.html", "html/ser_epi_map_2018.html", "html/ser_epi_map_2017.html",
                "html/ser_epi_map_2016.html", "html/ser_epi_map_2015.html", "html/ser_epi_map_2014.html")
names(table_site) <- c("2019", "2018", "2017", "2016", "2015", "2014")

bsselect(table_site, type = "iframe", frame_height=550, style="btn-primary", show_tick=TRUE, height=0)
```
